### 2023-09-14 paper/sec-dis-pseudodata.tex
updated yields

Several observations can be derived from Table~\ref{tab:integrated_rates}.
%
First, one appreciates the large increase in statistics from
the Run III experiments to the FPF ones, with for example a factor of
$\sim$ 250 increase in the muon neutrino yield between FASER$\nu$ and
FASER$\nu$2.
%
Second, the muon-neutrino scattering yield dominates over electron neutrino scattering by a factor
between 2 and 3, though the precise value of this ratio is affected by the large theory uncertainties
affecting forward electron neutrino production.
%
Third, charm production  represents around 15\% of the inclusive
yields, with both FASER$\nu$2 and FLArE100 resulting in around
40k recorded charm-production events.
%
Note that this result assumes $D$-meson tagging capabilities,
and if only dimuon events can be recorded
the yields would be reduced by a factor of 10.
%
Fourth, FASER$\nu$2 and FLArE100 lead to the largest absolute
yields of the FPF experiments, with a total of around 370k and 550k (non-tau) neutrino DIS events respectively, with 37k and 90k
events expected instead for AdvSND-far and for FLArE10.

>>>>

Several observations can be derived from Table~\ref{tab:integrated_rates}.
%
First, one appreciates the large increase in statistics from
the Run III experiments to the FPF ones, with for example a factor of
$\sim$ 250 increase in the muon neutrino yield between FASER$\nu$ and
FASER$\nu$2.
%
Second, the muon-neutrino scattering yield dominates over electron neutrino scattering by a factor
between 2 and 3, though the precise value of this ratio is affected by the large theory uncertainties
affecting forward electron neutrino production.
%
Third, charm production  represents around 15\% of the inclusive
yields, with both FASER$\nu$2 and FLArE100 resulting in around
80k recorded charm-production events.
%
Note that this result assumes $D$-meson tagging capabilities,
and if only dimuon events can be recorded
the yields would be reduced by a factor of 10.
%
Fourth, FASER$\nu$2 and FLArE100 lead to the largest absolute
yields of the FPF experiments, with a total of around 680k and 1.1M (non-tau) neutrino DIS events respectively, with 74k and 170k
events expected instead for AdvSND-far and for FLArE10.
